---
title: "Data Anlysis"
author: "Richard Lim"
date: '2022-10-04'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#loading necessary libraries
library(tidyverse)
```

```{r}
#Reading in subscription and visit data sets
subscriptions <- read.csv("/Users/richardlim/Desktop/subscriptions.csv")
visits <- read.csv("/Users/richardlim/Desktop/visits.csv")
#combining data sets by "account_id"
total <- merge(subscriptions, visits, by = "account_id")
```

## Question 1: How much revenue did each region generate within the time frame covered by the data sets?
```{r}
#replacing na values with )
total[is.na(total)] <- 0

#showing different regions
#table(total$region)

#Isolating by Regions
northAmerica <- total[total$region == "US/Canada", ]
cat("US/Canda total revenue:", sum(northAmerica$revenue), "\n")

asia <- total[total$region == "Asia", ]
cat("Asia total revenue:", sum(asia$revenue),"\n")

latinAmerica <- total[total$region == "Latin America", ]
cat("Latin America total revenue:", sum(latinAmerica$revenue),"\n")

EU_ME_A <- total[total$region == "Europe, Middle East, & Africa (Non-English)", ]
cat("Europe, Middle East, & Africa (Non-English) total revenue:", sum(EU_ME_A$revenue),"\n")

english_speaking <- total[total$region == "Other English-Speaking Countries", ]
cat("Other English-Speaking Countries total revenue:", sum(english_speaking$revenue),"\n")

```

## Question 2: Which channel had the highest revenue per visit? What was its revenue per visit?
```{r}
#showing different channels and number of visits
#table(total$channel)

#isolating channel when entry is "display"
display <- total[total$channel == "display", ]
#calculating revenue per visit by adding all revenue and dividing by total visits
display_revenue_per_visit <- (sum(display$revenue) / 1202)
cat("Revenue per visit for Display channel:", display_revenue_per_visit, "\n")

email <- total[total$channel == "email",]
email_revenue_per_visit <- (sum(email$revenue) / 887)
cat("Revenue per visit for Email channel:", email_revenue_per_visit, "\n")

organic_search <- total[total$channel == "organic search",]
osearch_revenue_per_visit <- (sum(organic_search$revenue) / 4029)
cat("Revenue per visit for Organic Search channel:", osearch_revenue_per_visit, "\n")

paid_search <- total[total$channel == "paid search", ]
psearch_revenue_per_visit <- (sum(paid_search$revenue)/ 3324)
cat("Revenue per visit for Paid Search channel:", psearch_revenue_per_visit, "\n")

parter_referral <- total[total$channel == "partner referral", ]
pReferral_revenue_per_visit <- (sum(parter_referral$revenue)/ 1700)
cat("Revenue per visit for Partner Referral channel:", pReferral_revenue_per_visit, "\n")

social <- total[total$channel == "social", ]
social_revenue_per_visit <- (sum(social$revenue)/ 199)
cat("Revenue per visit for Social channel:", social_revenue_per_visit, "\n")

video <- total[total$channel == "video", ]
video_revenue_per_visit <- (sum(video$revenue)/ 2271)
cat("Revenue per visit for Social channel:", video_revenue_per_visit, "\n")

cat("The channel that had the highest revenue per visit was Display with a revenue per visit of", display_revenue_per_visit)
```

## Question 3: Which landing page had the highest overall conversion rate (% of visitors that go on to become paying subscribers)? What was its conversion rate?
```{r}
#showing different landing pages and number of users who went to each
#table(total$landing_page)

#isolating A values from landing_page
A_page <- total[total$landing_page == "A", ]
#getting rid of people without subscriptions from A landing page 
A_subscriptions <- A_page[!(A_page$subscription_start_date==""), ]
#calculating conversion rate
A_conversion_rate <- 100 * (count(A_subscriptions) / count(A_page))
cat("Conversion rate for Landing page A is:", toString(A_conversion_rate), "\n")

B_page <- total[total$landing_page == "B", ]
B_subscriptions <- B_page[!(B_page$subscription_start_date==""), ]
B_conversion_rate <- 100 * (count(B_subscriptions) / count(B_page))
cat("Conversion rate for Landing page B is:", toString(B_conversion_rate), "\n")

C_page <- total[total$landing_page == "C", ]
C_subscriptions <- C_page[!(C_page$subscription_start_date==""), ]
C_conversion_rate <- 100 * (count(C_subscriptions) / count(C_page))
cat("Conversion rate for Landing page C is:", toString(C_conversion_rate), "\n")

D_page <- total[total$landing_page == "D", ]
D_subscriptions <- D_page[!(D_page$subscription_start_date==""), ]
D_conversion_rate <- 100 * (count(D_subscriptions) / count(D_page))
cat("Conversion rate for Landing page D is:", toString(D_conversion_rate), "\n")

E_page <- total[total$landing_page == "E", ]
E_subscriptions <- E_page[!(E_page$subscription_start_date==""), ]
E_conversion_rate <- 100 * (count(E_subscriptions) / count(E_page))
cat("Conversion rate for Landing page E is:", toString(E_conversion_rate), "\n")

F_page <- total[total$landing_page == "F", ]
F_subscriptions <- F_page[!(F_page$subscription_start_date==""), ]
F_conversion_rate <- 100 * (count(F_subscriptions) / count(F_page))
cat("Conversion rate for Landing page F is:", toString(F_conversion_rate), "\n")

G_page <- total[total$landing_page == "G", ]
G_subscriptions <- G_page[!(G_page$subscription_start_date==""), ]
G_conversion_rate <- 100 * (count(G_subscriptions) / count(G_page))
cat("Conversion rate for Landing page G is:", toString(G_conversion_rate), "\n")

H_page <- total[total$landing_page == "H", ]
H_subscriptions <- H_page[!(H_page$subscription_start_date==""), ]
H_conversion_rate <- 100 * (count(H_subscriptions) / count(H_page))
cat("Conversion rate for Landing page H is:", toString(H_conversion_rate), "\n")

I_page <- total[total$landing_page == "I", ]
I_subscriptions <- I_page[!(I_page$subscription_start_date==""), ]
I_conversion_rate <- 100 * (count(I_subscriptions) / count(I_page))
cat("Conversion rate for Landing page I is:", toString(I_conversion_rate), "\n")

J_page <- total[total$landing_page == "J", ]
J_subscriptions <- J_page[!(J_page$subscription_start_date==""), ]
J_conversion_rate <- 100 * (count(J_subscriptions) / count(J_page))
cat("Conversion rate for Landing page J is:", toString(J_conversion_rate), "\n")

cat("Landing page H had the highest conversion rate with a rate of", toString(H_conversion_rate))
```

## Question 4: Did any regions have a different top converting landing page (as compared to the previous answer)? If so, please list them along with their top landing page and its conversion rate.
```{r}
###############
# Asia Region #
###############

#isolating Asia region from all A Landing Page
asia_A_page <- A_page[A_page$region == "Asia", ]; #toString(count(asia_A_page))
#people with subscriptions from Asia region from A landing page
asia_A_subscriptions <- asia_A_page[!(asia_A_page$subscription_start_date==""), ]; #toString(count(asia_A_subscriptions))
cat("Asia's conversion rate for landing page A is", 100 * 149 / 241, "\n")

asia_B_page <- B_page[B_page$region == "Asia", ]; #toString(count(asia_B_page))
asia_B_subscriptions <- asia_B_page[!(asia_B_page$subscription_start_date==""), ]; #toString(count(asia_B_subscriptions))
cat("Asia's conversion rate for landing page B is", 100 * 197 / 324, "\n")

asia_C_page <- C_page[C_page$region == "Asia", ]; #toString(count(asia_C_page))
asia_C_subscriptions <- asia_C_page[!(asia_C_page$subscription_start_date==""), ]; #toString(count(asia_C_subscriptions))
cat("Asia's conversion rate for landing page C is", 100 * 121 / 198, "\n")

asia_D_page <- D_page[D_page$region == "Asia", ]; #toString(count(asia_D_page))
asia_D_subscriptions <- asia_D_page[!(asia_D_page$subscription_start_date==""), ]; #toString(count(asia_D_subscriptions))
cat("Asia's conversion rate for landing page D is", 100 * 183 / 311, "\n")

asia_E_page <- E_page[E_page$region == "Asia", ]; #toString(count(asia_E_page))
asia_E_subscriptions <- asia_E_page[!(asia_E_page$subscription_start_date==""), ]; #toString(count(asia_E_subscriptions))
cat("Asia's conversion rate for landing page E is", 100 * 468 / 732, "\n")

asia_F_page <- F_page[F_page$region == "Asia", ]; #toString(count(asia_F_page))
asia_F_subscriptions <- asia_F_page[!(asia_F_page$subscription_start_date==""), ]; #toString(count(asia_F_subscriptions))
cat("Asia's conversion rate for landing page F is", 100 * 65 / 101, "\n")

asia_G_page <- G_page[G_page$region == "Asia", ]; #toString(count(asia_G_page))
asia_G_subscriptions <- asia_G_page[!(asia_G_page$subscription_start_date==""), ]; #toString(count(asia_G_subscriptions))
cat("Asia's conversion rate for landing page G is", 100 * 150 / 236, "\n")

asia_H_page <- H_page[H_page$region == "Asia", ]; #toString(count(asia_H_page))
asia_H_subscriptions <- asia_H_page[!(asia_H_page$subscription_start_date==""), ]; #toString(count(asia_H_subscriptions))
cat("Asia's conversion rate for landing page H is", 100 * 82 / 118, "\n")

asia_I_page <- I_page[I_page$region == "Asia", ]; #toString(count(asia_I_page))
asia_I_subscriptions <- asia_I_page[!(asia_I_page$subscription_start_date==""), ]; #toString(count(asia_I_subscriptions))
cat("Asia's conversion rate for landing page I is", 100 * 191 / 306, "\n")

asia_J_page <- J_page[J_page$region == "Asia", ]; #toString(count(asia_J_page))
asia_J_subscriptions <- asia_J_page[!(asia_J_page$subscription_start_date==""), ]; #toString(count(asia_J_subscriptions))
cat("Asia's conversion rate for landing page J is", 100 * 153 / 269, "\n")
print("Landing Page H still has the highest conversion rate for Asia")
```

```{r}
#################
# Latin America #
#################

#isolating Latin America region from all A Landing Page
la_A_page <- A_page[A_page$region == "Latin America", ]; #toString(count(la_A_page))
#people with subscriptions from Asia region from A landing page
la_A_subscriptions <- la_A_page[!(la_A_page$subscription_start_date==""), ]; #toString(count(la_A_subscriptions))
cat("Latin America's conversion rate for landing page A is", 100 * 253 / 376, "\n")

la_B_page <- B_page[B_page$region == "Latin America", ]; #toString(count(la_B_page))
la_B_subscriptions <- la_B_page[!(la_B_page$subscription_start_date==""), ]; #toString(count(la_B_subscriptions))
cat("Latin America's conversion rate for landing page B is", 100 * 274 / 460, "\n")

la_C_page <- C_page[C_page$region == "Latin America", ]; #toString(count(la_C_page))
la_C_subscriptions <- la_C_page[!(la_C_page$subscription_start_date==""), ]; #toString(count(la_C_subscriptions))
cat("Latin America's conversion rate for landing page C is", 100 * 163 / 247, "\n")

la_D_page <- D_page[D_page$region == "Latin America", ]; #toString(count(la_D_page))
la_D_subscriptions <- la_D_page[!(la_D_page$subscription_start_date==""), ]; #toString(count(la_D_subscriptions))
cat("Latin America's conversion rate for landing page D is", 100 * 304 / 491, "\n")

la_E_page <- E_page[E_page$region == "Latin America", ]; #toString(count(la_E_page))
la_E_subscriptions <- la_E_page[!(la_E_page$subscription_start_date==""), ]; #toString(count(la_E_subscriptions))
cat("Latin America's conversion rate for landing page E is", 100 * 435 / 628, "\n")

la_F_page <- F_page[F_page$region == "Latin America", ]; #toString(count(la_F_page))
la_F_subscriptions <- la_F_page[!(la_F_page$subscription_start_date==""), ]; #toString(count(la_F_subscriptions))
cat("Latin America's conversion rate for landing page F is", 100 * 65 / 108, "\n")

la_G_page <- G_page[G_page$region == "Latin America", ]; #toString(count(la_G_page))
la_G_subscriptions <- la_G_page[!(la_G_page$subscription_start_date==""), ]; #toString(count(la_G_subscriptions))
cat("Latin America's conversion rate for landing page G is", 100 * 136 / 201, "\n")

la_H_page <- H_page[H_page$region == "Latin America", ]; #toString(count(la_H_page))
la_H_subscriptions <- la_H_page[!(la_H_page$subscription_start_date==""), ]; #toString(count(la_H_subscriptions))
cat("Latin America's conversion rate for landing page H is", 100 * 123 / 189, "\n")

la_I_page <- I_page[I_page$region == "Latin America", ]; #toString(count(la_I_page))
la_I_subscriptions <- la_I_page[!(la_I_page$subscription_start_date==""), ]; #toString(count(la_I_subscriptions))
cat("Latin America's conversion rate for landing page I is", 100 * 204 / 298, "\n")

la_J_page <- J_page[J_page$region == "Latin America", ]; #toString(count(la_J_page))
la_J_subscriptions <- la_J_page[!(la_J_page$subscription_start_date==""), ]; #toString(count(la_J_subscriptions))
cat("Latin America's conversion rate for landing page J is", 100 * 182 / 320, "\n")
print("Landing page E has the highest conversion rate with a rate of 69.26752 for Latin America")
```

```{r}
#############
# US/Canada #
#############

#isolating US/Canada region from all A Landing Page
na_A_page <- A_page[A_page$region == "US/Canada", ]; #toString(count(na_A_page))
#people with subscriptions from Asia region from A landing page
na_A_subscriptions <- na_A_page[!(na_A_page$subscription_start_date==""), ]; #toString(count(na_A_subscriptions))
cat("US/Canada's conversion rate for landing page A is", 100 * 160 / 265, "\n")

na_B_page <- B_page[B_page$region == "US/Canada", ]; #toString(count(na_B_page))
na_B_subscriptions <- na_B_page[!(na_B_page$subscription_start_date==""), ]; #toString(count(na_B_subscriptions))
cat("US/Canada's conversion rate for landing page B is", 100 * 157 / 308, "\n")

na_C_page <- C_page[C_page$region == "US/Canada", ]; #toString(count(na_C_page))
na_C_subscriptions <- na_C_page[!(na_C_page$subscription_start_date==""), ]; #toString(count(na_C_subscriptions))
cat("US/Canada's conversion rate for landing page C is", 100 * 136 / 249, "\n")

na_D_page <- D_page[D_page$region == "US/Canada", ]; #toString(count(na_D_page))
na_D_subscriptions <- na_D_page[!(na_D_page$subscription_start_date==""), ]; #toString(count(na_D_subscriptions))
cat("US/Canada's conversion rate for landing page D is", 100 * 175 / 334, "\n")

na_E_page <- E_page[E_page$region == "US/Canada", ]; #toString(count(na_E_page))
na_E_subscriptions <- na_E_page[!(na_E_page$subscription_start_date==""), ]; #toString(count(na_E_subscriptions))
cat("US/Canada's conversion rate for landing page E is", 100 * 425 / 784, "\n")

na_F_page <- F_page[F_page$region == "US/Canada", ]; #toString(count(na_F_page))
na_F_subscriptions <- na_F_page[!(na_F_page$subscription_start_date==""), ]; #toString(count(na_F_subscriptions))
cat("US/Canada's conversion rate for landing page F is", 100 * 47 / 96, "\n")

na_G_page <- G_page[G_page$region == "US/Canada", ]; #toString(count(na_G_page))
na_G_subscriptions <- na_G_page[!(na_G_page$subscription_start_date==""), ]; #toString(count(na_G_subscriptions))
cat("US/Canada's conversion rate for landing page G is", 100 * 149 / 246, "\n")

na_H_page <- H_page[H_page$region == "US/Canada", ]; #toString(count(na_H_page))
na_H_subscriptions <- na_H_page[!(na_H_page$subscription_start_date==""), ]; #toString(count(na_H_subscriptions))
cat("US/Canada's conversion rate for landing page H is", 100 * 115 / 167, "\n")

na_I_page <- I_page[I_page$region == "US/Canada", ]; #toString(count(na_I_page))
na_I_subscriptions <- na_I_page[!(na_I_page$subscription_start_date==""), ]; #toString(count(na_I_subscriptions))
cat("US/Canada's conversion rate for landing page I is", 100 * 178 / 322, "\n")

na_J_page <- J_page[J_page$region == "US/Canada", ]; #toString(count(na_J_page))
na_J_subscriptions <- na_J_page[!(na_J_page$subscription_start_date==""), ]; #toString(count(na_J_subscriptions))
cat("US/Canada's conversion rate for landing page J is", 100 * 151 / 265, "\n")

print("Landing Page H still has the highest conversion rate for US/Canada")
```

```{r}
###############################################
# Europe, Middle East, & Africa (Non-English) #
###############################################

#isolating Europe, Middle East, & Africa (Non-English) region from all A Landing Page
eu_A_page <- A_page[A_page$region == "Europe, Middle East, & Africa (Non-English)", ]; #toString(count(eu_A_page))
#people with subscriptions from Asia region from A landing page
eu_A_subscriptions <- eu_A_page[!(eu_A_page$subscription_start_date==""), ]; #toString(count(eu_A_subscriptions))
cat("Europe, Middle East, & Africa (Non-English)'s conversion rate for landing page A is", 100 * 215 / 339, "\n")

eu_B_page <- B_page[B_page$region == "Europe, Middle East, & Africa (Non-English)", ]; #toString(count(eu_B_page))
eu_B_subscriptions <- eu_B_page[!(eu_B_page$subscription_start_date==""), ]; #toString(count(eu_B_subscriptions))
cat("Europe, Middle East, & Africa (Non-English)'s conversion rate for landing page B is", 100 * 155 / 283, "\n")

eu_C_page <- C_page[C_page$region == "Europe, Middle East, & Africa (Non-English)", ]; #toString(count(eu_C_page))
eu_C_subscriptions <- eu_C_page[!(eu_C_page$subscription_start_date==""), ]; #toString(count(eu_C_subscriptions))
cat("Europe, Middle East, & Africa (Non-English)'s conversion rate for landing page C is", 100 * 116 / 200, "\n")

eu_D_page <- D_page[D_page$region == "Europe, Middle East, & Africa (Non-English)", ]; #toString(count(eu_D_page))
eu_D_subscriptions <- eu_D_page[!(eu_D_page$subscription_start_date==""), ]; #toString(count(eu_D_subscriptions))
cat("Europe, Middle East, & Africa (Non-English)'s conversion rate for landing page D is", 100 * 168 / 296, "\n")

eu_E_page <- E_page[E_page$region == "Europe, Middle East, & Africa (Non-English)", ]; #toString(count(eu_E_page))
eu_E_subscriptions <- eu_E_page[!(eu_E_page$subscription_start_date==""), ]; #toString(count(eu_E_subscriptions))
cat("Europe, Middle East, & Africa (Non-English)'s conversion rate for landing page E is", 100 * 243 / 423, "\n")

eu_F_page <- F_page[F_page$region == "Europe, Middle East, & Africa (Non-English)", ]; #toString(count(eu_F_page))
eu_F_subscriptions <- eu_F_page[!(eu_F_page$subscription_start_date==""), ]; #toString(count(eu_F_subscriptions))
cat("Europe, Middle East, & Africa (Non-English)'s conversion rate for landing page F is", 100 * 37 / 68, "\n")

eu_G_page <- G_page[G_page$region == "Europe, Middle East, & Africa (Non-English)", ]; #toString(count(eu_G_page))
eu_G_subscriptions <- eu_G_page[!(eu_G_page$subscription_start_date==""), ]; #toString(count(eu_G_subscriptions))
cat("Europe, Middle East, & Africa (Non-English)'s conversion rate for landing page G is", 100 * 78 / 136, "\n")

eu_H_page <- H_page[H_page$region == "Europe, Middle East, & Africa (Non-English)", ]; #toString(count(eu_H_page))
eu_H_subscriptions <- eu_H_page[!(eu_H_page$subscription_start_date==""), ]; #toString(count(eu_H_subscriptions))
cat("Europe, Middle East, & Africa (Non-English)'s conversion rate for landing page H is", 100 * 103 / 166, "\n")

eu_I_page <- I_page[I_page$region == "Europe, Middle East, & Africa (Non-English)", ]; #toString(count(eu_I_page))
eu_I_subscriptions <- eu_I_page[!(eu_I_page$subscription_start_date==""), ]; #toString(count(eu_I_subscriptions))
cat("Europe, Middle East, & Africa (Non-English)'s conversion rate for landing page I is", 100 * 131 / 211, "\n")

eu_J_page <- J_page[J_page$region == "Europe, Middle East, & Africa (Non-English)", ]; #toString(count(eu_J_page))
eu_J_subscriptions <- eu_J_page[!(eu_J_page$subscription_start_date==""), ]; #toString(count(eu_J_subscriptions))
cat("Europe, Middle East, & Africa (Non-English)'s conversion rate for landing page J is", 100 * 160 / 247, "\n")

print("Landing page J has the highest conversion rate with a rate of 64.77733 for Europe, Middle East, & Africa (Non-English)")
```

```{r}
####################################
# Other English-Speaking Countries #
####################################

#isolating Other English-Speaking Countries region from all A Landing Page
es_A_page <- A_page[A_page$region == "Other English-Speaking Countries", ]; #toString(count(es_A_page))
#people with subscriptions from Asia region from A landing page
es_A_subscriptions <- es_A_page[!(es_A_page$subscription_start_date==""), ]; #toString(count(es_A_subscriptions))
cat("Other English-Speaking Countries's conversion rate for landing page A is", 100 * 143 / 248, "\n")

es_B_page <- B_page[B_page$region == "Other English-Speaking Countries", ]; #toString(count(es_B_page))
es_B_subscriptions <- es_B_page[!(es_B_page$subscription_start_date==""), ]; #toString(count(es_B_subscriptions))
cat("Other English-Speaking Countries's conversion rate for landing page B is", 100 * 127 / 243, "\n")

es_C_page <- C_page[C_page$region == "Other English-Speaking Countries", ]; #toString(count(es_C_page))
es_C_subscriptions <- es_C_page[!(es_C_page$subscription_start_date==""), ]; #toString(count(es_C_subscriptions))
cat("Other English-Speaking Countries's conversion rate for landing page C is", 100 * 107 / 202, "\n")

es_D_page <- D_page[D_page$region == "Other English-Speaking Countries", ]; #toString(count(es_D_page))
es_D_subscriptions <- es_D_page[!(es_D_page$subscription_start_date==""), ]; #toString(count(es_D_subscriptions))
cat("Other English-Speaking Countries's conversion rate for landing page D is", 100 * 177 / 319, "\n")

es_E_page <- E_page[E_page$region == "Other English-Speaking Countries", ]; #toString(count(es_E_page))
es_E_subscriptions <- es_E_page[!(es_E_page$subscription_start_date==""), ]; #toString(count(es_E_subscriptions))
cat("Other English-Speaking Countries's conversion rate for landing page E is", 100 * 266 / 439, "\n")

es_F_page <- F_page[F_page$region == "Other English-Speaking Countries", ]; #toString(count(es_F_page))
es_F_subscriptions <- es_F_page[!(es_F_page$subscription_start_date==""), ]; #toString(count(es_F_subscriptions))
cat("Other English-Speaking Countries's conversion rate for landing page F is", 100 * 54 / 91, "\n")

es_G_page <- G_page[G_page$region == "Other English-Speaking Countries", ]; #toString(count(es_G_page))
es_G_subscriptions <- es_G_page[!(es_G_page$subscription_start_date==""), ]; #toString(count(es_G_subscriptions))
cat("Other English-Speaking Countries's conversion rate for landing page G is", 100 * 75 / 131, "\n")

es_H_page <- H_page[H_page$region == "Other English-Speaking Countries", ]; #toString(count(es_H_page))
es_H_subscriptions <- es_H_page[!(es_H_page$subscription_start_date==""), ]; #toString(count(es_H_subscriptions))
cat("Other English-Speaking Countries's conversion rate for landing page H is", 100 * 85 / 133, "\n")

es_I_page <- I_page[I_page$region == "Other English-Speaking Countries", ]; #toString(count(es_I_page))
es_I_subscriptions <- es_I_page[!(es_I_page$subscription_start_date==""), ]; #toString(count(es_I_subscriptions))
cat("Other English-Speaking Countries's conversion rate for landing page I is", 100 * 76 / 116, "\n")

es_J_page <- J_page[J_page$region == "Other English-Speaking Countries", ]; #toString(count(es_J_page))
es_J_subscriptions <- es_J_page[!(es_J_page$subscription_start_date==""), ]; #toString(count(es_J_subscriptions))
cat("Other English-Speaking Countries's conversion rate for landing page J is", 100 * 73 / 131, "\n")

print("Landing page I has the highest conversion rate with a rate of 65.51724 for Other English-Speaking Countries")
```

## Question 5: Which region had the highest direct subscription rate (% of visitors that start a subscription directly without doing a trial)? What was its direct subscription rate?
```{r}
#getting rid of people without subscriptions in US/Canada
na_direct_sub <- northAmerica[!(northAmerica$subscription_start_date==""), ]; #toString(count(na_direct_sub))
#getting rid of people who had trials from people with subscriptions in US/Canada
na_direct_sub1 <- northAmerica[(northAmerica$trial_end_date==""), ]; #toString(count(na_direct_sub1))
#calculating direct subscription rate by dividing # of people without subscriptions in the US/Canada region from # of people with subscriptions but without trials
cat("US/Canada region has a direct subscription rate of", 100 * 880 / 1693, "\n")

asia_direct_sub <- asia[!(asia$subscription_start_date==""), ]; #toString(count(asia_direct_sub))
asia_direct_sub1 <- asia[(asia$trial_end_date==""), ]; #toString(count(asia_direct_sub1))
cat("Asia region has a direct subscription rate of", 100 * 1042 / 1759, "\n")

la_direct_sub <- latinAmerica[!(latinAmerica$subscription_start_date==""), ]; #toString(count(la_direct_sub))
la_direct_sub1 <- latinAmerica[(latinAmerica$trial_end_date==""), ]; #toString(count(la_direct_sub1))
cat("Latin America region has a direct subscription rate of", 100 * 1121 / 2139, "\n")

eu_direct_sub <- EU_ME_A[!(EU_ME_A$subscription_start_date==""), ]; #toString(count(eu_direct_sub))
eu_direct_sub1 <- EU_ME_A[(EU_ME_A$trial_end_date==""), ]; #toString(count(eu_direct_sub1))
cat("Europe, Middle East, & Africa (Non-English) region has a direct subscription rate of", 100 * 629 / 1406, "\n")

es_direct_sub <- english_speaking[!(english_speaking$subscription_start_date==""), ]; #toString(count(es_direct_sub))
es_direct_sub1 <- english_speaking[(english_speaking$trial_end_date==""), ]; #toString(count(es_direct_sub1))
cat("Other English-Speaking Countries region has a direct subscription rate of", 100 * 516 / 1183, "\n")

print("Asia has the highest direct subscription rate with a rate of 59.2382%")
```

## Question 6: Which region had the highest trial start rate (% of visitors that start a trial, regardless of whether those users ultimately cancel or become paying subscribers)? What was its trial start rate?
```{r}
#taking total count of people in US/Canada region 
#toString(count(northAmerica))
#removing everyone who did not start a trial 
na_trial <- northAmerica[!(northAmerica$trial_start_date==""),]; #toString(count(na_trial))
cat("US/Canada region has a trial start rate of", 100 * 2156 / 3036, "\n")

#toString(count(asia))
asia_trial <- asia[!(asia$trial_start_date==""),]; #toString(count(asia_trial))
cat("Asia region has a trial start rate of", 100 * 1794 / 2836, "\n")

#toString(count(latinAmerica))
la_trial <- latinAmerica[!(latinAmerica$trial_start_date==""),]; #toString(count(la_trial))
cat("Latin America region has a trial start rate of", 100 * 2197 / 3318, "\n")

#toString(count(EU_ME_A))
eu_trial <- EU_ME_A[!(EU_ME_A$trial_start_date==""),]; #toString(count(eu_trial))
cat("Europe, Middle East, & Africa (Non-English) region has a trial start rate of", 100 * 1740 / 2369, "\n")

#toString(count(english_speaking))
es_trial <- english_speaking[!(english_speaking$trial_start_date==""),]; #toString(count(es_trial))
cat("Other English-Speaking Countries region has a trial start rate of", 100 * 1537 / 2053, "\n")

print("Other English-Speaking Countries region had the highest trial start rate with a rate of 74.86605%")
```

## Question 7: Which region had the highest trial conversion rate (% of trials that start a subscription)? What was its trial conversion rate?
```{r}
#counting how many people in US/Canada region have a trial
#toString(count(na_trial))
#removing people who do not have a subscription from people in US/Canada region who have a trial and counting
trial_conv_na <- na_trial[!(na_trial$subscription_start_date==""), ]; #toString(count(trial_conv_na))
cat("US/Canada region has a trial conversion rate of", 100 * 813 / 2156, "\n")

#toString(count(asia_trial))
trial_conv_asia <- asia_trial[!(asia_trial$subscription_start_date==""), ];# toString(count(trial_conv_asia))
cat("Asia region has a trial conversion rate of", 100 * 717 / 1794, "\n")

#toString(count(la_trial))
trial_conv_la <- la_trial[!(la_trial$subscription_start_date==""), ]; #toString(count(trial_conv_la))
cat("Latin America region has a trial conversion rate of", 100 * 1018 / 2197, "\n")

#toString(count(eu_trial))
trial_conv_eu <- eu_trial[!(eu_trial$subscription_start_date==""), ]; #toString(count(trial_conv_eu))
cat("Europe, Middle East, & Africa (Non-English) region has a trial conversion rate of", 100 * 777 / 1740, "\n")

#toString(count(es_trial))
trial_conv_es <- es_trial[!(es_trial$subscription_start_date==""), ]; #toString(count(trial_conv_es))
cat("Other English-Speaking Countries region has a trial conversion rate of", 100 * 667 / 1537, "\n")

print("Latin America has the highest trial conversion rate with a rate of 46.33591%")
```
